Trinity: A Language for Multi-View Architecture Description and Control

### 2017-07-29 sigplanconf-template.tex
added beta code snippet

\documentclass[preprint]{sigplanconf}
% The following \documentclass options may be useful:
% preprint       Remove this option only once the paper is in final form.
%  9pt           Set paper in  9-point type (instead of default 10-point)
% 11pt           Set paper in 11-point type (instead of default 10-point).
% numbers        Produce numeric citations with natbib (instead of default author/year).
% authorversion  Prepare an author version, with appropriate copyright-space text.
\usepackage{amsmath}

\newcommand{\cL}{{\cal L}}

@@

>>>>

\documentclass[preprint]{sigplanconf}
% The following \documentclass options may be useful:
% preprint       Remove this option only once the paper is in final form.
%  9pt           Set paper in  9-point type (instead of default 10-point)
% 11pt           Set paper in 11-point type (instead of default 10-point).
% numbers        Produce numeric citations with natbib (instead of default author/year).
% authorversion  Prepare an author version, with appropriate copyright-space text.
\usepackage{amsmath}
\usepackage{listings}
\usepackage{xcolor}

\colorlet{light-gray}{gray!20}
\newcommand{\cL}{{\cal L}}

@@

\begin{figure}

	\begin{lstlisting}[frame=single, backgroundcolor=\color{light-gray}, basicstyle=\footnotesize\ttfamily, numbers=left, numberstyle=\tiny\color{black},caption= {Simple 3-tier web application architecture}]
component Client
	port getInfo: requires CSIface

component Server
	port sendInfo: provides CSIface

external component DB
	port dbIface: target DBModule

connector JDBCCtr
	val connectionString: String

architecture 
	components
		RequestHandler ch
		DB db

connectors 
	JDBCCtr jdbcCtr

attachments
	connect rh.dbIface and db.dbIface 
		with jdbcCtr

bindings 
	sendInfo is rh.sendInfo

architecture 	
	components
		Client client
		Server server

	connectors
		JSONCtr jsonCtr

	attachments 
		Connect client.getInfo 
		and server.sendInfo with jsonCtr

	entryPoints
		Client: start
	\end{lstlisting}

\end{figure}
